---
title: "dynamicSnow Example"
author: "Russell S. Pierce"
date: "04/06/2015"
output: html_document
---

Note, the example may assume you are running Linux for the purposes
of simulating a node failure, but dynamicSnow does not require that
you are running Linux, as far as I know, but it has been tested most
in a Linux environment.

```{r}
library(parallel)
if (!require(devtools)) {install.packages("devtools");library(devtools)}
if (!require(dynamicSnow)) {install_github("drknexus/dynamicSnow");library(dynamicSnow)}
```

Let's say we make a cluster.
```{r}
cl <- makePSOCKcluster(rep("localhost",2))
clusterEvalQ(cl,"Hi")
```

But then we decide we need one more node...
```{r}
cl[[3]] <- parallel:::newPSOCKnode("localhost", rank = 3)
clusterEvalQ(cl,"Hi")
```

But, something bad happens, and one of our nodes dies...
```{r}
nodePIDs <- parSapply(cl,1:3,function(x) {Sys.getpid()})
# now we kill one of the nodes
library(tools)
pskill(nodePIDs[2])
```

Then bad things happen, we can't get any of our results back!
```{r}
# clusterEvalQ(cl,"Hi")
```

How do we know there is a problem?
```{r}
all(checkPulse(cl))
```

How do we fix that problem?
```{r}
cl <- healCluster(cl)
```

Are we really recovered?
```{r}
clusterEvalQ(cl,"Hi")
```

Clean up the example
```{r}
stopCluster(cl)
```